Pandemic Pass? Treaty Derogations and Human Rights Practices During COVID-19

### 2023-03-03 manuscript/manuscript.qmd
No need for fill scale

```{r fig-preds-prelim, fig.width=12, fig.height=6, out.width="100%"}
#| include: true
#| echo: false
#| layout-ncol: 1
#| fig-cap: "Predicted effects of imposing specific emergency public health measures over first 15 months of the COVID pandemic, split by whether states formally derogated from the ICCPR"
#| fig-subcap:
#|   - "Predicted probabilities"
#|   - "Contrasts between predicted probabilities"

prelim_plots <- prelim_plot_data %>% 
  mutate(pred_plot = map2(pred_data, nice, ~{
    .x %>% 
      ggplot(aes(x = year_week_day, y = .epred, ymin = .lower, ymax = .upper,
                 color = derogation_ineffect, fill = after_scale(color), 
                 group = forcats::fct_rev(ordered(.width)))) +
      geom_lineribbon(alpha = 0.3) +
      scale_color_manual(values = c(clrs[1], clrs[8])) +
      scale_fill_manual(values = c(clrs[1], clrs[8])) +
      scale_x_date(date_breaks = "2 months", date_labels = "%b\n%Y") +
      scale_y_continuous(labels = label_percent()) +
      labs(x = NULL, y = "Predicted probability", 
           color = "Derogation in effect", fill = "Derogation in effect",
           title = .y) +
      theme_pandem()
  })) %>% 
  mutate(mfx_plot = map2(mfx_data, nice, ~{
    .x %>% 
      mutate(across(c(draw, .lower, .upper), ~ . * 100)) %>% 
      ggplot(aes(x = year_week_day, y = draw, ymin = .lower, ymax = .upper,
                 group = forcats::fct_rev(ordered(.width)))) +
      geom_lineribbon(alpha = 0.25, fill = clrs[5], color = clrs[5]) +
      scale_x_date(date_breaks = "2 months", date_labels = "%b\n%Y") +
      labs(x = NULL,
           y = "Percentage point difference\nin probability of policy",
           title = .y) +
      theme_pandem()
  }))

>>>>

```{r fig-preds-mfx-prelim, fig.width=12, fig.height=6, out.width="100%", cache=FALSE}
#| include: true
#| echo: false
#| layout-ncol: 1
#| fig-cap: "Predicted effects of imposing specific emergency public health measures over first 15 months of the COVID pandemic, split by whether states formally derogated from the ICCPR"
#| fig-subcap:
#|   - "Predicted probabilities"
#|   - "Contrasts between predicted probabilities"

prelim_plots <- prelim_plot_data %>% 
  mutate(pred_plot = map2(pred_data, nice, ~{
    .x %>% 
      ggplot(aes(x = year_week_day, y = .epred, ymin = .lower, ymax = .upper,
                 color = derogation_ineffect, fill = after_scale(color), 
                 group = forcats::fct_rev(ordered(.width)))) +
      geom_lineribbon(alpha = 0.3) +
      scale_color_manual(values = c(clrs[1], clrs[8])) +
      scale_x_date(date_breaks = "2 months", date_labels = "%b\n%Y") +
      scale_y_continuous(labels = label_percent()) +
      labs(x = NULL, y = "Predicted probability", 
           color = "Derogation in effect", fill = "Derogation in effect",
           title = .y) +
      theme_pandem()
  })) %>% 
  mutate(mfx_plot = map2(mfx_data, nice, ~{
    .x %>% 
      mutate(across(c(draw, .lower, .upper), ~ . * 100)) %>% 
      ggplot(aes(x = year_week_day, y = draw, ymin = .lower, ymax = .upper,
                 group = forcats::fct_rev(ordered(.width)))) +
      geom_lineribbon(alpha = 0.25, fill = clrs[5], color = clrs[5]) +
      scale_x_date(date_breaks = "2 months", date_labels = "%b\n%Y") +
      labs(x = NULL,
           y = "Percentage point difference\nin probability of policy",
           title = .y) +
      theme_pandem()
  }))
